%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Frontend Engineer} % Job title
    {LINE Corporation} % Organization
    {Kyoto, Japan} % Location
    {Mar. 2019 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Tech lead in an eKYC service (frontend team with 3 members), made the decisions for tech stack and frontend architecture. (React, Redux/Redux-Toolkit, Styled Component)}
        \item {Created product from scratch and implemented features with team members.}
        \item {Coached junior members to solve problems and found the target.}
        \item {Made the refactoring plan. (migrated to React Hooks and fixed Redux issues)}
        \item {Lead team to fix typing issues during Javascript to Typescript migration, and fit to Typescript guideline.}
        \item {Used OpenAPI spec, and applied auto-generated OpenAPI client, created API draft with server teams.}
        \item {Created design system with Storybook and built reusable components.}
        \item {Discussed design issues with design team in retrospective meeting.}
        \item {Built End-to-End Testing flow with Cypress in order to reduce QA team's effort.}
        \item {Created CI/CD flow. (Docker, Drone, AWS S3, CDN configuration)}
        \item {Did some small open-source contributions for libraries which we are using.}
        \item {Improved development experience continuously. (Made enhancement for development environment, such as linter, prettier...etc)}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Anfu Solutions Inc.} % Organization
    {Taipei, Taiwan} % Location
    {Jan. 2017 - Feb. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built first MVP product with Ruby on Rails. (a web service related to real estate market)}
        \item {Created the web site architecture with AWS. (EC2, Opsworks, RDS, ElastiCache, SES...etc)}
        \item {Built GIS featuress with PostGIS/Postgres.}
        \item {Implemented core product for external bank customers.}
        \item {Discussed the requirement of product with customers.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
  {Software Engineer (Part-time)} % Job title
  {KerjaDulu} % Organization
  {Taipei, Taiwan} % Location
  {Dec. 2013 - Aug. 2016} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Created new features with Ruby on Rails. (a recruiting web service)}
      \item {Refactored web pages with AngularJS.}
      \item {Built the architecture to send large amount of marketing emails. (2 millions / day)}
      \item {Did some enhancement for SEO. (Sent sitemap regularly, fixed issues for DOM structure and meta tags)}
      \item {Help migrate cloud environment from Heroku to AWS.}
    \end{cvitems}
  }

%---------------------------------------------------------

  \cventry
  {Engineering Intern} % Job title
  {Mozilla Corporation} % Organization
  {Taipei, Taiwan} % Location
  {Aug. 2013 - Oct. 2013} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Intenship program in FirefoxOS team.}
      \item {Created unit tests and dev tools for product development.}
    \end{cvitems}
  }

%---------------------------------------------------------
\end{cventries}
